AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-10 Paper/main.tex
10-10 paper

The dataset we used for training, validation and testing is built by \citeauthor{wang2019optimized} \citep{wang2019optimized}. 
We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively, from its source data.

>>>>

The dataset we used for training, validation and testing is built by \citeauthor{wang2019optimized} \citep{wang2019optimized}. 
We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively, from its source data. 
As far as we know, the best performance on this dataset is the DeepHF of \citeauthor{wang2019optimized} currently, which base on deep learning and bidirectional LSTM architecture. 
DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively. 
Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \cite{MuhammadRafid2020}. 
They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively (without any hyperparameter tuning).
